Finite Property Convex Elicitation Paper

### 2019-01-21 cvx-fin.tex
minor edits

\raf{This is missing a bunch of stuff from Jessie's notes on equivalence of definitions, the existence of a link function, etc}

@@

\begin{conjecture}
  Let $\mathrm{elic}_{Pcvx}$ denote the elicitation complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.
  Then for all finite elicitable properties $\Gamma$, we conjecture $\mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$.
\end{conjecture}

>>>>

\raf{This is missing a bunch of stuff: equivalence of possible definitions, existence of a (weak) link function, etc}

@@

Let $\mathrm{elic}_{embed}$ denote the elicitation complexity with respect to embeddings, $\mathrm{elic}_{Pcvx}$ the complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.

\begin{conjecture}
  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
\end{conjecture}

\subsection*{Acknowledgements}
We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
